Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-07 SupportingInformation.Rmd
addingfig and tables from beta variation results : asym sensitivity

pdf("./Results/asym_sens_results/beta_0.1_asym_sen.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

@@

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AIC_w","relLTdep_AICw","relUTdep_AIC_w","p_CvM","p_KS","Numboot_success")
bg <- intToUtf8(0x03B2) 
cname<-paste0(bg, c("_0.1","_0.1_decrease_T","_-0.1","_-0.1_decrease_T","_0.9","_0.9_decrease_T","_-0.9","_-0.9_decrease_T"))
colnames(summary_stat)<-cname

stat_npa_asym_beta_0.1_beta_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible beta variation

@@

>>>>

pdf("./Results/asym_sens_results/beta_0.1_asym_sens.pdf")
ans_beta_0.1<-plotter_asym_sens_beta_varn(N=N,rho=rho,alpha=alpha,beta=0.1,numkeep_last=numkeep_last,ploton=T)
dev.off()

@@

summary_stat<-as.data.frame(matrix(NA,7,8),stringsAsFactors = F) # Table for model selection summary
rownames(summary_stat)<-c("bestcop_AICw","N_AIC_w","relLTdep_AICw","relUTdep_AIC_w","p_CvM","p_KS","Numboot_success")
bg <- intToUtf8(0x03B2) 
cnm<-c("_0.1","_0.1_decrease_T","_-0.1","_-0.1_decrease_T","_0.9","_0.9_decrease_T","_-0.9","_-0.9_decrease_T")
cname<-paste0(bg,cnm)
colnames(summary_stat)<-cname

stat_npa_asym_beta_0.1_beta_0.9<-vector(mode = "list", length = 8) # initializing list to store NPA results for all possible beta variation
names(stat_npa_asym_beta_0.1_beta_0.9)<-cname

@@

![results for model selection \label{fig_ms_asym_beta_0.1}](./Results/asym_sens_results/beta_0.1_asym_sens.pdf){ width=40%, height=40% }

![results for model selection \label{fig_ms_asym_beta_0.9}](./Results/asym_sens_results/beta_0.9_asym_sens.pdf){ width=40%, height=40% }

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}

knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asym. sensitivity \\label{tab_summary_stat_asym_sens}")
```

```{r tab_stat_npa_asym,echo=F,results="asis"}
#knitr::opts_knit$set(kable.force.latex = TRUE)
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_beta_0.1_beta_0.9.RDS")

for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  temp2<-knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste("beta",cnm[i]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence."))
  print(temp2)
  cat("\\newpage")
}
```
